---
title: "Rita Giordano"
description: |
  Data visualisation and scientific illustration
site: distill::distill_website
css: "css/strapless.css"
header-includes:
    - \renewcommand{\contentsname}{}
---
<!-- Remove margin under images -->
<!-- <style> -->
<!-- d-article div.sourceCode pre { -->
<!--   background: #dae7f1; -->
<!-- } -->

<!-- code { -->
<!--   background-color: #dae7f1; -->
<!-- } -->

<!-- d-article pre  { -->
<!--   background-color: #dae7f1; -->
<!-- } -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```
I'm Rita a data visualisation consultant and scientific illustrator. I have more than thirteen years of experience in data analysis and visualisation. 

## What I can do for you
Do you have data to visualise? I will find the best way to visualise them. 

Do you have data to analyse and visualise? Let's discuss about which analysis would be the best and how I will visualise your data.

Do you need and R packages for your company? I have several years of experience in creating R packages for internal project. In the last years, I have also developed two packages available on CRAN 

Do you need a graphical abstract or a scientific illustration? I'm here to listen to you and create the illustration that best fit your needs.

I code in R and d3.js and I can create static and interactive visualisations.

```{r}
# Read in projects csv file
first <- read_csv("data/first_page.csv")
```

```{r projects, echo=FALSE, layout="l-body-outset"}
 first[1:2,] %>%
   bs4cards::cards(
     title = title,
     #text = description,
     link = url,
     image = src,
     layout = "label-above",
     spacing = 5,
     #width = 1,
     width = "row-cols-2",
     border_width = 0,
     #layout = "inset-bottom",
     label_colour = c("#ffffffaa", "#ffffffaa"),
     breakpoint = 5,
     #border_colour = "#ffffffaa"

  )
```

## What I cannot do for you
I don't work on project that involves only data science without data visualisation.

I don't do dashboard.

