---
title: "World fertility rate"
description: |
  How the fertility rate changed in the last 60 years.
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# htmltools::includeHTML("test.html")
```

I was interested to compare the fertility rate in the 2010s with the 1960s. The bar chart shows a decrease for each level of income of fertility rates in the 2010s. 
High income countries present a lower fertility rate than low income countries. 
It seems that the fertility rate decreases in places where women have access to higher education.

```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width= 10, fig.height=6}
library(readxl)
library(tidyverse)
library(GenderInfer)

data <- read_excel("../../DataViz_TheGuardian/Fertility Rate Data.xlsx")

count_income <- data %>% count(IncomeGroup)

data_2 <- data %>% group_by(IncomeGroup) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

income <- data_2 %>% pivot_longer(!IncomeGroup,
                                  names_to = "Years",
                                  values_to = "count") %>%
  mutate(Years = as.numeric(Years))

## define year range to make the comparison
range <- seq(1960,1969)

baselines<- bind_cols(income %>%
  filter(IncomeGroup == "High income",
         Years %in% range) %>%
  summarise(baseline_high = mean(count)),
  income %>%
    filter(IncomeGroup == "Upper middle income",
           Years %in% range) %>%
    summarise(baseline_upper = mean(count)),
  income %>%
    filter(IncomeGroup == "Lower middle income",
           Years %in% range) %>%
    summarise(baseline_lower = mean(count)),
  income %>%
    filter(IncomeGroup == "Low income",
           Years %in% range) %>%
    summarise(baseline_low = mean(count))
  )

baselines_df <- baselines %>%
  pivot_longer(cols = starts_with("baseline"),
                names_to = "baseline",
               values_to = "value") %>%
  mutate(baseline = gsub("baseline_", "", baseline)) %>%
  mutate(baseline = case_when(baseline == "high" ~ "High income",
                              baseline == "upper" ~ "Upper middle income",
                              baseline == "lower" ~ "Lower middle income",
                              baseline == "low" ~ "Low income",
                              TRUE ~ baseline))
## create data with
range_2010 <- seq(2010, 2019)

fertility <- income %>%
  filter(Years %in% range_2010) %>%
  group_by(IncomeGroup) %>%
  mutate(values = mean(count)) %>%
  distinct(IncomeGroup, values)

ggplot() +
  geom_bar(aes(x = reorder(baseline, -value), y = value, fill = "#D7191C"), data = baselines_df,
           width = 0.55, stat = "identity", show.legend = FALSE) +
  geom_bar(aes(x = IncomeGroup, y = values, fill = "#512B58"),
           data = fertility ,
           stat = "identity", width = 0.4) +
  scale_fill_manual(values=c(alpha("#D7191C", .4), alpha("#512B58", .5)),
                    labels = c("2010-2019", "1960-1969"), name = "Years range") +
  guides(fill = guide_legend(override.aes = list(alpha = 0.5))) +
  theme(axis.title.x = element_text( size=20),
        axis.text.x  = element_text(size=16),
        axis.title.y = element_text( size=20),
        axis.text.y  = element_text(size=16),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 12)) +
  theme(text = element_text(color = "navy"),
          panel.background = element_rect(fill = "white"),
          panel.grid.major.x = element_line(color = "grey"),
          panel.grid.minor.x = element_line(color = "grey",
                                            linetype = "dashed"),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank(),
          axis.ticks = element_blank(),
          strip.background = element_rect(fill = "white", color = "grey"),
        legend.position="bottom", legend.direction="horizontal") +
  xlab("Income") + ylab("Fertility rate") + coord_flip() +
  ggtitle("World fertility: comparision between 1960s and 2010s ") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  labs(caption = "Source: The Data World Bank")

```

With Flourish I realised an interactive visualisation that shows the fertility rate by income worldwide. By changing the filter it is possible to spot the differences between the countries for the year 2019. 

```{r}
htmltools::includeHTML("flourish2.html")
```






